%!TEX root = Main.tex
\documentclass[Main]{subfiles}

\begin{document}

\chapter{Conclusion}
Our finished product is a PC client and server console application with the following contents. As this project builds upon our project in assignment 1, the parts that overlap will not be mentioned.
\begin{itemize}
\item Server
	\begin{itemize}
		\item Made asynchronous using the leader/follower pattern
		\item Reactor improved to handle asynchronous calls, i.e. able to deactivate and reactive handlers
		\begin{itemize}
				\item A locking mechanism was put in place for concurrency
				\item Promotion mechanism for electing new leaders
				\item Leader/Follower event handler to wrap all other event handlers.
		\end{itemize}
		\item Server part of an acceptor/connector pattern, i.e. the acceptor part. 
		\item Service handlers are templated in acceptor, so that an acceptor for each service should be created.
	\end{itemize}
\item Client
	\begin{itemize}
		\item Server part of an acceptor/connector pattern, i.e. the connector part.
		\item Connector made fully synchronous, i.e. all behaviour not needed i a synchronous enviroment were removed.
	    \item Service handlers are templated in connector, so that a connector for each service should be created.
	\end{itemize}
\end{itemize}
We have done a small bit of extra-work on this assignement, meaning we have chosen to only implement a synchronous connector, and made some creative decision on the concurrency of the leader/follower pattern (i.e. sleeps to make sure that threads are ready).
\end{document}