%!TEX root = Main.tex
\documentclass[Main]{subfiles}

\begin{document}

\chapter{Introduction}
\section{Requirements}
This journal seeks to describe exercises one to three from the course TIARDI as done by group two. \\
The main task of the assignment consisted of making a server/client application based on the reactor- and wrapperfacade pattern. These patterns will be described in more detail in the next chapter. The journal will generally be split into three parts in each chapter, unless something else is specified. These parts will describe the work done in exercise one, two and three separately, but also describing how they fit in the whole implementation of the reactor pattern. \\
The work has been completed in visual studio, using C++11.

\subsection{Requirements of assignment 1}
This assignment was the base of all further work as it implemented the wrapper-facade abstraction of a socket connection. This should serve as the basis of all socket communication in later assignments. There was only created a windows type wrapper-facade, but could, with minimal work, be extended to e.g. linux. (This will be described further in the "Patterns" section).

\subsection{Requirements of assignment 2}
This assignment should function as the server of the reactor pattern and should furthermore use the wrapper-facade implementation of socket connections done in assignment 1. 

\subsection{Requirements of assignment 3}
This assignment should finalize the work done in assignment 2, adding a client to the reactor pattern and thereby finishing it. the client connections should also be created using event-handlers, and use the client part of the wrapper-facade.

\subfile{Patterns}


\end{document}